### 2022-04-30 draft.tex
Deploying to gh-pages from @ EcoComplex/TrophicResourcesEdaphic@998e8dfc1a5d305ceb53ee8f8db89b682812f316 🚀

The use of the natural variation of \textbf{stable isotopes} (F) as
empirical evidence of the use of trophic resources is based on the study
of isotopic signatures; the isotopic signature of \$\delta\$15N informs
about the trophic level of the invertebrate and that of \$\delta\$13C
will indicate the proportion of trophic resources consumed, but the
potential trophic resources need to be chosen previously to the isotopic
analysis. (Tiunov 2007; Maraun et al.~2011; Potapov, Tiunov, and Scheu
2019; Potapov et al.~2019) also, the potential of this tool is such that
inferences can even be made about the metabolic pathways of biomolecules
(Pollierer et. Al. 2019, Pollierer \& Scheu 2021; Chamberlain et. Al.
2006).

>>>>

The use of the natural variation of \textbf{stable isotopes} (F) as
empirical evidence of the use of trophic resources is based on the study
of isotopic signatures; the isotopic signature of \(\delta\text{15N}\)
informs about the trophic level of the invertebrate and that of
\(\delta\text{13C}\) will indicate the proportion of trophic resources
consumed, but the potential trophic resources need to be chosen
previously to the isotopic analysis. (Tiunov 2007; Maraun et al.~2011;
Potapov, Tiunov, and Scheu 2019; Potapov et al.~2019) also, the
potential of this tool is such that inferences can even be made about
the metabolic pathways of biomolecules (Pollierer et. Al. 2019,
Pollierer \& Scheu 2021; Chamberlain et. Al. 2006).
